The request is to create a Quarto `targets` pipeline that uses Semantic Scholar to grab data for network graph creation. Below is a hypothetical Quarto `targets` pipeline written in R that could fulfill such a request. This is a basic framework and would require the user to have the necessary API keys and libraries to interact with Semantic Scholar. Please note that for a real-world scenario, error handling, rate limiting, and other API constraints would need to be considered.

```{r}
library(targets)
library(tarchetypes)
library(jsonlite)
library(httr)
library(igraph)
library(networkD3)
library(reticulate)
```

```{r}
# User-provided list of identifiers (e.g., paper DOIs, titles, Semantic Scholar IDs)
identifiers <- c("identifier1", "identifier2", "identifier3")
```

```{r}
# Function to get data from Semantic Scholar using an identifier
get_paper_data <- function(identifier) {
  # Semantic Scholar API URL with identifier placeholder
  url <- paste0("https://api.semanticscholar.org/v1/paper/", identifier)
  response <- httr::GET(url)
  
  # Check if the request was successful
  if (response$status_code == 200) {
    content <- httr::content(response, "text", encoding = "UTF-8")
    json_data <- jsonlite::fromJSON(content)
  } else {
    # Return NULL or raise an error if response is not successful
    NULL
  }
}
```

```{r}
test_paper <- get_paper_data("DOI:10.18653/v1/N18-3011")
```



```{r}
# Define targets
list(
  tar_target(identifiers, identifiers),
  # Use map to iterate over identifiers and get paper data
  tar_map(
    values = tarchetypes::tar_bind(identifiers),
    # Call get_paper_data for each identifier
    names = names(identifiers),
    pattern = map(identifiers),
    tar_target(paper_data, get_paper_data(identifiers))
  )
)
```



```{python}
import requests
r2 = requests.get('https://api.semanticscholar.org/datasets/v1/release/latest').json()
print(r2['release_id'])
```
```{python}
r_id = requests.get("https://api.semanticscholar.org/datasets/v1/release/2024-04-16").json()
```

